Paper Figs

### 2023-03-22 graphs_newt_snakes/Paper_figs.Rmd
I made some more figures that look really nice

grid.arrange(main_plot, bloan, extra_plot, ncol = 2, 
             layout_matrix=cbind(c(1,1),c(2,3)))

@@

@@

file1 = GA1_cor[which(1:nrow(GA1_cor) %% 2 != 0) , ]
file2 = cost_grade_cor
file3 = interrate_grade
title = "Spatial Phenotype Correlation Across Different Simulation Conditions"
subt = " "
exp_labeles=c("Flat Map", "Cost Gradent Map", "Interaction Gradent Map")
x_label = "Simulations"
y_label = "Spatila Correlation"
min_gen = 40000
max_gen = 50000

boxplot_cors_by_gen_col_rep(file1, file2, file3, title, subt, x_label, y_label, min_gen, max_gen)

@@

@@

  plot <-  ggplot(file_long) +
  ggtitle(title, subtitle = subt)+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(sim, level=c("D", "C", "B", "H", "G", "L", "A", "F", "K", "P", "E", "J", "I", "O", "N", "M")), y=as.numeric(value), fill=factor(name)))+
  theme(plot.title = element_text(size=5)) +
  #xlim(-1.1, 1.1)+
  scale_fill_manual(values =c("darkred", "steelblue"), labels=c('Newt', 'Snake'))+
    labs(fill = " ")+
    #scale_fill_manual(values =c("darkred", "purple", "steelblue"), labels=c('Newt Advantage', 'No Advantage', 'Snake Advantage'))+
    labs(fill = " ")+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      title =element_text(size=8, face='bold'))

@@

@@

>>>>

plot(main_plot)

#grid.arrange(main_plot, bloan, extra_plot, ncol = 2, 
#             layout_matrix=cbind(c(1,1),c(2,3)))

@@

cost_grade_no_interact_cor<- read.csv("~/Desktop/no_interaction_cost_grade/all_cor.txt" , header = TRUE)
cost_grade_no_interact_cor$group_rep <- paste0(cost_grade_no_interact_cor$snake_mu_rate, "_", cost_grade_no_interact_cor$snake_mu_effect_sd,"_",cost_grade_no_interact_cor$newt_mu_rate, "_", cost_grade_no_interact_cor$newt_mu_effect_sd, "_", cost_grade_no_interact_cor$rep)
cost_grade_no_interact_cor$group <- paste0(cost_grade_no_interact_cor$snake_mu_rate, "_", cost_grade_no_interact_cor$snake_mu_effect_sd,"_",cost_grade_no_interact_cor$newt_mu_rate, "_", cost_grade_no_interact_cor$newt_mu_effect_sd)
cost_grade_no_interact_cor$sim=LETTERS[factor(cost_grade_no_interact_cor$group)]
cost_grade_no_interact_cor$exp="Cost Gradent Map No Interaction"

snake_change_cor<- read.csv("~/Desktop/snake_change/all_cor.txt" , header = TRUE)
snake_change_cor$group_rep <- paste0(snake_change_cor$snake_mu_rate, "_", snake_change_cor$snake_mu_effect_sd,"_",snake_change_cor$newt_mu_rate, "_", snake_change_cor$newt_mu_effect_sd, "_", snake_change_cor$rep)
snake_change_cor$group <- paste0(snake_change_cor$snake_mu_rate, "_", snake_change_cor$snake_mu_effect_sd,"_",snake_change_cor$newt_mu_rate, "_", snake_change_cor$newt_mu_effect_sd)
snake_change_cor$sim=LETTERS[factor(snake_change_cor$group)]
snake_change_cor$exp="Snake Gradent Map"

newt_change_cor<- read.csv("~/Desktop/newt_change/all_cor.txt" , header = TRUE)
newt_change_cor$group_rep <- paste0(newt_change_cor$snake_mu_rate, "_", newt_change_cor$snake_mu_effect_sd,"_",newt_change_cor$newt_mu_rate, "_", newt_change_cor$newt_mu_effect_sd, "_", newt_change_cor$rep)
newt_change_cor$group <- paste0(newt_change_cor$snake_mu_rate, "_", newt_change_cor$snake_mu_effect_sd,"_",newt_change_cor$newt_mu_rate, "_", newt_change_cor$newt_mu_effect_sd)
newt_change_cor$sim=LETTERS[factor(newt_change_cor$group)]
newt_change_cor$exp="Newt Gradent Map"

@@

boxplot_cors_by_gen_col_rep_6_file <- function(file1, file2, file3, file4, file5, file6, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
   file1$snake_newt <- paste0(file1$snake_mu_rate, "_", file1$snake_mu_effect_sd, "_", file1$newt_mu_rate, "_", file1$newt_mu_effect_sd)
   file2$snake_newt <- paste0(file2$snake_mu_rate, "_", file2$snake_mu_effect_sd, "_", file2$newt_mu_rate, "_", file2$newt_mu_effect_sd)
   file3$snake_newt <- paste0(file3$snake_mu_rate, "_", file3$snake_mu_effect_sd, "_", file3$newt_mu_rate, "_", file3$newt_mu_effect_sd)
    file4$snake_newt <- paste0(file4$snake_mu_rate, "_", file4$snake_mu_effect_sd, "_", file4$newt_mu_rate, "_", file4$newt_mu_effect_sd)
   file5$snake_newt <- paste0(file5$snake_mu_rate, "_", file5$snake_mu_effect_sd, "_", file5$newt_mu_rate, "_", file5$newt_mu_effect_sd)
   file6$snake_newt <- paste0(file6$snake_mu_rate, "_", file6$snake_mu_effect_sd, "_", file6$newt_mu_rate, "_", file6$newt_mu_effect_sd)
file <- rbind(file1, file2, file3, file4, file5, file6)

file$exp = factor(file$exp, levels=c("Flat Map", "Cost Gradent Map No Interaction", "Cost Gradent Map", "Snake Gradent Map", "Interaction Gradent Map", "Newt Gradent Map"))

  plot <-  ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(sim, level=c('Sims', "F","G","H","J","K","L","N","O","P")), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), fill=factor(cor_score)))+
  theme(plot.title = element_text(size=5)) +
  #xlim(-1.1, 1.1)+
    geom_hline(yintercept=real_snewt_cor, linetype="dashed")+
  facet_wrap(~exp, ncol=2)+
  scale_fill_manual(values =c("darkolivegreen3", "cadetblue2"), labels=c('Low Mutatinal Variance', 'Coevolution'))+
    labs(fill = " ")+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      title =element_text(size=8, face='bold'))

file1 = GA1_cor
file2 = cost_grade_cor
file3 = interrate_grade
file4 = cost_grade_no_interact_cor
file5 = snake_change_cor
file6 = newt_change_cor
title = "Spatial Phenotype Correlation Across Different Simulation Conditions"
subt = " "
exp_labeles=c("Flat Map", "Cost Gradent Map", "Interaction Gradent Map")
x_label = "Simulations"
y_label = "Spatila Correlation"
min_gen = 40000
max_gen = 50000

boxplot_cors_by_gen_col_rep(file1, file2, file3, title, subt, x_label, y_label, min_gen, max_gen)
boxplot_cors_by_gen_col_rep_6_file(file1, file2, file3, file4, file5, file6, title, subt, x_label, y_label, min_gen, max_gen)

@@

file$coevo_score[file$sim %in% newt_adv] = "Newt Advantage"
file$coevo_score[file$sim %in% mid] = "No Advantage"
file$coevo_score[file$sim %in% snake_adv] = "Snake Advantage"
file$newt_snake_pheno_avg= (file$newt_pheno_change+file$snake_pheno_change)/2
file$rect_type = ifelse(file$sim == "A" | file$sim == "B"| file$sim == "C" | file$sim == "D"| file$sim == "E"| file$sim == "I"| file$sim == "M", "False","True")

target=c("D", "C", "B", "H", "G", "L", "A", "F", "K", "P", "E", "J", "I", "O", "N", "M")

file$xmin = match(file$sim, target) - 0.5

file$xmax = match(file$sim, target) + 0.5

@@

plot <-   ggplot(file_long) +
  ggtitle(title, subtitle = subt)+
  xlab(x_label) + ylab(y_label)+
geom_boxplot(aes(x=factor(sim, level=c("D", "C", "B", "H", "G", "L", "A", "F", "K", "P", "E", "J", "I", "O", "N", "M")), y=as.numeric(value), fill=factor(name)))+
  geom_rect(aes(xmin = as.numeric(xmin), xmax = as.numeric(xmax), ymin = -Inf, ymax = Inf, fill = rect_type)) +
  scale_fill_manual( values =c("darkred", "steelblue", "white","aliceblue" ), breaks = c('newt_pheno_change', 'snake_pheno_change', "True", "False"),  labels = c('Newt', 'Snake', "True", "False"))+ #labels=c("False",'Newt', 'Snake', "True")
      geom_boxplot(aes(x=factor(sim, level=c("D", "C", "B", "H", "G", "L", "A", "F", "K", "P", "E", "J", "I", "O", "N", "M")), y=as.numeric(value), fill=factor(name)),show.legend = FALSE)+
     theme(plot.title = element_text(size=5)) +
    labs(fill = " ")+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      title =element_text(size=8, face='bold'))

@@

boxplot_coevo_slope_small_exp_color <- function(file1, file2, file3, title, subt, x_label, y_label){

  plot <-  ggplot(file) +
  ggtitle(title, subtitle = subt)+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(sim), y=as.numeric(newt_snake_pheno_avg), fill=factor(exp)))+
  theme(plot.title = element_text(size=5)) +
  #xlim(-1.1, 1.1)+
  scale_fill_manual(values =c("darkolivegreen1", "azure2", "darkorange3"), labels=c("No Interaction", "No Heritability", "Coevolution Flat Map"))+
    labs(fill = " ")+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      title =element_text(size=8, face='bold'))

@@

boxplot_coevo_slope_small_exp_color(file1, file2, file3, title, subt, x_label, y_label)
